Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-04 analysis/paper/sim_survey_paper.Rmd
Finish drafting presentation

- Feedback and advice: Alejandro Buren, Mariano Koen-Alonso, Karen Dwyer, Joanne Morgan, Geoff Evans, Don Power, Brian Healey, Martha Robertson, Danny Ings, Don Stansbury, Mark Simpson, Derek Osborne, Peter Upward, Brad Squires, Dwayne Pittman, Paul Higdon
- Dave Cote for a review of a previous version of this manuscript

>>>>

- Feedback and advice: Alejandro Buren, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Derek Osborne, Dwayne Pittman, Don Power, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward
- Dave Cote for a review of a previous version of this manuscript

### 2018-09-04 analysis/presentation/sim_survey_presentation.Rmd
Finish drafting presentation

- Increasing sub-sampling effort may be an inefficient means of improving population estimates
    - Especially problimatic if sub-sampling affects primary sampling effort

@@

- Todo

>>>>

Increasing sub-sampling effort may be an inefficient means of improving population estimates

- Large catches are relatively infrequent
    - Samples in large sets are not independent
        - If the goal is to maximize information, it is likely better to stop collecting psudoreplicates and, instead, focus efforts on other species or the next set

@@

>- **Feedback and advice:** Alejandro Buren, Dave Cote, Karen Dwyer, Geoff Evans, Brian Healey, Paul Higdon, Danny Ings, Mariano Koen-Alonso, Joanne Morgan, Derek Osborne, Dwayne Pittman, Don Power, Martha Robertson, Mark Simpson, Brad Squires, Don Stansbury, Peter Upward, ...
>- **Support:** Fisheries and Oceans Canada and NSERC
